\section{Introduction}

AI coding agents are moving from suggestion engines to active participants in software development. Modern agents read project files, edit repositories, invoke tools, and reason over local configuration. Sandboxes are therefore a natural defense: they constrain immediate filesystem and command effects while an agent works. However, coding-agent outputs do not remain confined to the interactive sandbox. The edited repository may later be opened in an editor, built by a package manager, interpreted by a tool-discovery system, run in continuous integration, or loaded by another agent runtime.

This lifecycle creates a security gap. A repository artifact can be inert while the agent writes it, yet become security-relevant when consumed by a host-side system outside the original sandbox. Prior agent-security benchmarks study prompt injection in tool and web agents~\cite{agentdojo2024,wasp2025}, harmful multi-step agent behavior~\cite{agentharm2024}, coding-agent interfaces~\cite{sweagent2024}, or direct container sandbox escape capability~\cite{sandboxescapebench2026}. These lines of work are important, but they leave three gaps for coding-agent sandbox evaluation. \emph{G1: discovery}. Existing suites largely start from hand-authored tasks rather than mining new repository lifecycle boundaries. \emph{G2: semantics}. Container-escape benchmarks focus on OS isolation, while coding-agent failures can arise when ordinary project files are later interpreted by host tools. \emph{G3: evidence}. Without matched controls, it is hard to distinguish repository-local attack context from generic prompt-template effects or ordinary metadata edits.

We call this class \emph{semantic sandbox escape}. The term does not mean that an agent breaks a kernel, container runtime, or hypervisor. Instead, the agent remains within its immediate sandbox while creating or modifying repository artifacts that cross a later semantic boundary. Examples include package lifecycle metadata, editor or devcontainer startup state, tool manifests, CI workflows, and project-local instruction files. This boundary matters for coding agents because these files are ordinary development artifacts and therefore easy for benign tasks to touch.

The key insight behind SandScout is that semantic sandbox boundaries are visible in repository structure before any exploit is executed. Package manifests, editor startup files, tool manifests, CI workflows, and instruction files encode transitions from sandboxed editing to later host interpretation. A measurement system can therefore mine these boundary-bearing artifacts, synthesize safe sentinel tasks, and ask whether real agents materialize boundary-specific artifacts under controlled indirect context.

We present \emph{SandScout}, an automated method for mining and evaluating semantic sandbox escape candidates. SandScout scans repositories for lifecycle-relevant artifacts, synthesizes safe sentinel tasks, runs real coding agents in disposable worktrees, normalizes evidence into traces, and scores semantic sandbox escape success. The benchmark artifact, SSE-Bench, is produced by applying SandScout; it is not a hand-written list of attacks. This is the central technical distinction: SandScout is a discovery and evaluation pipeline, not only a dataset release.

Our prototype currently focuses on safe measurement. It never emits real exploit payloads. Instead, each task uses a fixed benign marker, \texttt{SSE\_BENIGN\_SENTINEL}, and the oracle checks whether the agent creates the boundary-specific sentinel file. This proxy is intentionally conservative. It cannot prove real-world exploitability, but it can measure whether repository-local context causes an agent to materialize a boundary-specific artifact. To support safe release, SandScout also scans tasks, prompts, outputs, and diffs for credential indicators, destructive commands, exploit payload indicators, and product-specific vulnerability claims.

This paper makes four contributions:
\begin{itemize}
    \item We define semantic sandbox escape as a lifecycle-boundary attack class for AI coding agents, separating it from prompt-only hijacking and kernel/container escape.
    \item We introduce SandScout, an automated miner and evaluation harness that discovers repository-level boundary candidates and synthesizes safe sentinel tasks from them.
    \item We implement a real-agent runner, trace oracle, and safety scanner that separate instruction uptake, artifact placement, triggerability, benign task completion, infrastructure failures, and unsafe-content findings.
    \item We provide preliminary evidence from Codex CLI: SandScout-mined indirect-context tasks produce sentinel placement across four boundary classes, while three matched no-note controls stay at zero and one control remains pending due to availability failures.
\end{itemize}
